An analysis of underlying relationships between factors related to operating costs and revenue in Australian vineyards.

### 2023-11-21 article.tex
backing up the article

\subsection{Data}
% 6049 samples - total
% 58 regions
% 10 years
% 
% 853 with reported profits
% 46 regions
% reported since 2018
Data used in this analysis were obtained from Sustainable Winegrowing Australia. Australia's national wine industry sustainability program. The program aims to support grape-growers and winemakers in demonstrating and improving their sustainability \citep{swaSustainableWingrowingAustralia2022}. Data recorded by SWA are entered manually by winegrowers using a web based interface tool. A total of 6049 observations were collected from 2012/2013 to 2021/2022 financial years, with each observation comprising 23 variables reflecting a vineyard's state for the given year (see Table \ref{tab:vars}). 
\par
\begin{table}[] 
 \label{tab:vars}
 \caption{Summary of variables used in the analysis. The recorded column indicate the number of values that were either greater than zero or that were not missing.}\label{tab:summary}
 \begin{tabular}{@{}ccccl@{}}
  \toprule
  \textbf{Variable} & \textbf{Units} & \textbf{Recorded} & \textbf{\begin{tabular}[c]{@{}c@{}}Number of\\ Classes\end{tabular}} & \\ \midrule
  Water Used & Mega Litres & 5846 & & \\
  Diesel & Litres & 5585 & & \\
  Biodiesel & Litres & 25 & & \\
  LPG & Litres & 958 & & \\
  Herbicide Spray & Times per year & 2026 & & \\
  Year & Class & 6049 & 10 & \\
  Disease & Class & 6049 & 2 & \\
  Region & Class & 6049 & 58 & \\
  Solar & Kilowatt Hours & 622 & & \\
  Irrigation Type & Class & 6049 & 20 & \\
  Petrol & Litres & 4309 & & \\
  Slashing & Times per year & 2290 & & \\
  Yield & Tonnes & 5935 & & \\
  Irrigation Energy & Class & 6049 & 16 & \\
  Area Harvested & Hectares & 6049 & & \\
  Electricity & Kilowatt Hours & 1014 & & \\
  Insecticide Spray & Times per year & 1092 & & \\
  Fertiliser & \begin{tabular}[c]{@{}c@{}}Kilograms \\ of Nitrogen\end{tabular} & 795 & & \\
  Fungicide Spray & Times per year & 2260 & & \\
  Cover Crop & Class & 6049 & 32 & \\
  Water Type & Class & 6049 & 39 & \\
  Grape Revenue & AUD & 853 & & \\
  Operating Costs & AUD & 853 & & \\ \bottomrule
  \end{tabular}
\end{table}
% FIXME: Add supplementary tables of all classes and another table of the summary statistics of continuous variables. Refer to this table to help with the paragraphs about one-hot encoding. A quick definition of one-hot encoding will also help!
The data originally contained only two multiclass variables: year and region. Variables that measured the same metric from different sources (such as water collected from rivers versus water from dams) were converted into multiclass variables representing the source through one-hot-encoding. Changing each variable class into a binary value, with one indicating the presence of the class and zero indicating its absence. Occurrences of multiple sources were defined as their own separate classes. Where a class variable had a recorded amount the total amount used from these variables was retained as a separate variable; for example water used (in Mega Litres ) was also included alongside water source.
\par
The variable region represented one of the 65 Geographical Indicator Regions (GI Region) used to describe different unique localised traits of vineyards across Australia \citep{hallidayAustralianWineEncyclopedia2009,oliverReviewSoilPhysical2013,soarClimateDriversRed2008}. Each region is explicitly defined under the Wine Australia Corporation Act of 1980 \citep{attorney-generalsdepartmentWineAustraliaCorporation2010}.
\par

@@

XGBoosted (eXtreme Gradient Boosting) trees, described in more detail below,  were created using the XGBoost library \citep{chenXGBoostScalableTree2016} in the Python Programming language \citep{g.vanrossumPythonTutorialTechnical1995}. XGBoosted trees are a boosted tree ensemble method that can be used to classify classes, or predict continuous response variables. They were chosen for this analysis as the data contained a mixture of class and continuous variables. Moreover, XGBoosted trees are unaffected by multicollinearity, and offer high predictive performance for a wide variety of purposes \citep{chenXGBoostScalableTree2016}.

@@

An XGBoosted tree was created for each variable to show how they interacted. Each tree included all variables except the economic variables (operating cost and revenue from grape sales), which were only included within their own trees as response variables. Separately profit (the difference between revenue and operational costs) was looked at in prior analyses (see appendix) but the results were not included due to low average loss values and model stability. This meant that every variable would have a measure of its importance to other variables (see Section \ref{sec:importance}), which was used to show the highly interrelated nature of variables within vineyards. The interaction between variables was illustrated using Sankey and Chord diagrams; with variable importance measures being used to show the strength of connection between the respective predictor variable and the response (see section \ref{sec:importance}).

@@

% FIXME: this section can be tightende/shortened a lot - moving some of the material into the supplementary section
Due to XGBoost creating a large amount of decision trees, the interpretability of these models is obfuscated by the intricate relationships within complicated ensembles. A measure of variable importance was the technique used to highlight a variables influence within the ensemble. Variable importance can be measured in multiple ways; we used the frequency of a variable appearing as a node within the ensemble as a measure of its importance. This measure was chosen as it connected a variable to the minimisation of its associated objective function. The measure of a variable's importance within this study can then be interpreted as how often a variable was the optimal choice in reducing the loss function of the ensemble. Importantly, multiclass variables being one-hot-encoded
% FIXME: make sure one-hot-encoding is well defined and rephrase this so it makes more sense (possibly define it earlier as suggested in the data section.)
are given an importance score for each individual class; for example, each specific region will have its own importance score.

@@

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% The Australian wine-growing industry is a rich and diverse landscape that is separated into multiple Geographical Indicator Regions. Each region describing unique reputations, qualities and varietals of wine produced there. While a great deal has been done regarding individual regional properties and traits, there has been little statistical insight into broader regional comparisons; due to a lack of cross-regional and in-depth data sources \citep{keithjonesAustralianWineIndustry2002,knightFirmResourcesDevelopment2019}. In this study we use Classification Trees to compare regional differences and how these differences relate to sustainable practices. 
% \newline
% FIXME: The first result should be in the langauge of the question. In the original document the first result presented was region, implying that the question is: 'are regions different?' which is not the forefocus of the article. The results need to be rearranged to show grossmargin and operating costs as more significant variables as they are the curious factors that we do not understand.

% FIXME: The irritating placement of the figures is due to the way latex uses the /ref function to determine where a figure should be. Have a google of this to overcome it as the figure placement is all over the shop.

@@

% This is possibly the connection between the presence of the Hunter Valley within the XGBoost ensemble that determined profit (see Figure \ref{fig:profit_sankey}). With this connection reflecting the restriction of possible strategies employable by winegrowers between different regions. % FIXME:  No this is because the hunter valley/tasmania get paid more / tonne.

@@

% Although less important in the XGBoost ensembles for profit, the variables: cover crops, and number of fungicide spraying and slashing passes are likely linked to broad environmental properties of regions (see Figure \ref{fig:region_sankey} and \ref{fig:profit_sankey}). Rainfall being related to vine fungal growth, disease and weed pressure. With cover crops being an effective and sustainable method to alleviate these issues \citep{delpuechAdaptingCoverCrop2018}. % FIXME: Re-structure this sentance.

@@

 \section{Variable summaries}

The Table \ref{cont_summary} below shows the ranges of each of the continuous variables:
% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
  \begin{tabular}{@{}lllllllll@{}}
  \toprule
   & count & mean & std & min & 0.25 & 0.5 & 0.75 & max \\ \midrule
  Vineyard Solar & 622 & 22916.89 & 104808 & 1 & 1170.75 & 5500 & 14866.25 & 2300000 \\
  Biodiesel & 25 & 6635.932 & 11768.832104 & 1 & 200 & 500 & 10000 & 37216 \\
  Fungicide Spray & 2260 & 7.724801 & 3.279794 & 1 & 6 & 7 & 9 & 68 \\
  LPG & 958 & 327.831399 & 861.538804 & 1 & 40 & 95.835 & 240 & 11950 \\
  Petrol & 4309 & 825.276809 & 1556.621119 & 1 & 135 & 306.66 & 903 & 38568 \\
  Insecticide Spray & 1092 & 1.707189 & 1.316042 & 0 & 1 & 1 & 2 & 12 \\
  Water Used & 5846 & 7301838 & 558206600 & 0.0007 & 13.2655 & 43 & 146.875 & 42680000000 \\
  Fertiliser & 795 & 91149.89 & 483913.4 & 1 & 560 & 4759.5 & 45148.5 & 11358000 \\
  Diesel & 5585 & 11677.070183 & 24380.588742 & 0.1267 & 1240 & 3850 & 12500 & 591000 \\
  Yield & 5935 & 772.902449 & 2175.113895 & 0.03 & 68 & 192.3 & 601.8795 & 72305 \\
  Herbicide Spray & 2026 & 2.646199 & 2.598899 & 0 & 2 & 2 & 3 & 103 \\
  Slashing & 2290 & 3.311485 & 1.826788 & 1 & 2 & 3 & 4 & 26 \\
  Electricity & 1014 & 58223.07 & 177626.3 & 0.019 & 2160 & 9637 & 36498.25 & 3000000 \\
  Area Harvested & 6049 & 66.52604 & 133.4525 & 2.220446E-16 & 10.13 & 24.5 & 66.8 & 2436.15 \\
  Grape Revenue & 875 & 377972 & 606286.8 & 1 & 76000 & 172964 & 386747 & 5700000 \\
  Operating Costs & 853 & 314187.1 & 511522.6 & 1 & 57315 & 140000 & 327408 & 4482828 \\ \bottomrule
  \end{tabular}
  \end{table}

  \section{water types}

@@

\section{cover crop types}
% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
  \begin{tabular}{@{}ll@{}}
  \toprule
  Cover crop types & frequency \\ \midrule
  permanent_cover_crop_volunteer_sward & 1822 \\
  permanent_cover_crop_non_native & 936 \\
  permanent_cover_crop_native & 490 \\
  annual_cover_crop & 479 \\
  groundwater and surface water dam & 406 \\
  annual_cover_crop and permanent_cover_crop_volunteer_sward & 309 \\
  bare_soil & 225 \\
  permanent_cover_crop_non_native and permanent_cover_crop_volunteer_sward & 214 \\
  annual_cover_crop and permanent_cover_crop_non_native & 169 \\
  bare_soil and permanent_cover_crop_volunteer_sward & 129 \\
  bare_soil and permanent_cover_crop_non_native & 115 \\
  annual_cover_crop and permanent_cover_crop_non_native and permanent_cover_crop_volunteer_sward & 101 \\
  bare_soil and annual_cover_crop & 93 \\
  permanent_cover_crop_native and permanent_cover_crop_volunteer_sward & 80 \\
  bare_soil and permanent_cover_crop_native & 78 \\
  annual_cover_crop and permanent_cover_crop_native & 78 \\
  permanent_cover_crop_native and permanent_cover_crop_non_native & 68 \\
  permanent_cover_crop_native and permanent_cover_crop_non_native and permanent_cover_crop_volunteer_sward & 44 \\
  annual_cover_crop and permanent_cover_crop_native and permanent_cover_crop_non_native and permanent_cover_crop_volunteer_sward & 44 \\
  bare_soil and annual_cover_crop and permanent_cover_crop_volunteer_sward & 33 \\
  bare_soil and permanent_cover_crop_non_native and permanent_cover_crop_volunteer_sward & 26 \\
  annual_cover_crop and permanent_cover_crop_native and permanent_cover_crop_volunteer_sward & 17 \\
  bare_soil and annual_cover_crop and permanent_cover_crop_native & 15 \\
  annual_cover_crop and permanent_cover_crop_native and permanent_cover_crop_non_native & 15 \\
  bare_soil and annual_cover_crop and permanent_cover_crop_non_native & 13 \\
  bare_soil and annual_cover_crop and permanent_cover_crop_native and permanent_cover_crop_non_native and permanent_cover_crop_volunteer_sward & 12 \\
  bare_soil and annual_cover_crop and permanent_cover_crop_non_native and permanent_cover_crop_volunteer_sward & 11 \\
  bare_soil and annual_cover_crop and permanent_cover_crop_native and permanent_cover_crop_non_native & 8 \\
  bare_soil and permanent_cover_crop_native and permanent_cover_crop_non_native & 7 \\
  bare_soil and permanent_cover_crop_native and permanent_cover_crop_volunteer_sward & 6 \\
  bare_soil and permanent_cover_crop_native and permanent_cover_crop_non_native and permanent_cover_crop_volunteer_sward & 4 \\
  bare_soil and annual_cover_crop and permanent_cover_crop_native and permanent_cover_crop_volunteer_sward and & 2 \\ \bottomrule
  \end{tabular}
  \end{table}

\section{irrigation type}

@@

  \section{irrigation energy type}

@@

  \section{year}
  % Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
  \begin{tabular}{@{}ll@{}}
  \toprule
  data_year_id & frequency \\ \midrule
  2021/2022 & 954 \\
  2020/2021 & 860 \\
  2019/2020 & 599 \\
  2012/2013 & 590 \\
  2013/2014 & 549 \\
  2015/2016 & 548 \\
  2014/2015 & 505 \\
  2017/2018 & 493 \\
  2016/2017 & 485 \\
  2018/2019 & 466 \\ \bottomrule
  \end{tabular}
  \end{table}

\section{giregion}
% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
  \begin{tabular}{@{}ll@{}}
  \toprule
  giregion & frequency \\ \midrule
  McLaren Vale & 1195 \\
  Barossa Valley & 584 \\
  Murray Darling & 521 \\
  Riverland & 472 \\
  Adelaide Hills & 454 \\
  Langhorne Creek & 347 \\
  Margaret River & 344 \\
  Coonawarra & 284 \\
  Padthaway & 202 \\
  Wrattonbully & 195 \\
  Clare Valley & 149 \\
  Yarra Valley & 122 \\
  Eden Valley & 92 \\
  Tasmania & 89 \\
  Swan Hill & 83 \\
  Grampians & 73 \\
  Orange & 72 \\
  Hunter Valley & 70 \\
  Bendigo & 53 \\
  Great Southern & 51 \\
  Rutherglen & 41 \\
  Robe & 36 \\
  Tumbarumba & 35 \\
  Mornington Peninsula & 32 \\
  King Valley & 32 \\
  Southern Fleurieu & 30 \\
  Heathcote & 29 \\
  Adelaide Plains & 25 \\
  Currency Creek & 24 \\
   & 23 \\
  Henty & 22 \\
  Canberra District & 21 \\
  Southern Flinders Ranges & 20 \\
  Upper Goulburn & 20 \\
  Mudgee & 20 \\
  Mount Benson & 20 \\
  Other & 19 \\
  Riverina & 18 \\
  Alpine Valleys & 15 \\
  Barossa Zone & 14 \\
  Pemberton & 12 \\
  Mount Gambier & 11 \\
  Blackwood Valley & 10 \\
  Kangaroo Island & 10 \\
  Big Rivers Zone Other & 9 \\
  Geographe & 7 \\
  Cowra & 6 \\
  Gundagai & 5 \\
  Strathbogie Ranges & 5 \\
  Glenrowan & 4 \\
  Geelong & 4 \\
  Swan District & 4 \\
  Goulburn Valley & 3 \\
  Beechworth & 3 \\
  Southern Highlands & 3 \\
  Macedon Ranges & 2 \\
  Pyrenees & 2 \\
  Sunbury & 1 \\ \bottomrule
  \end{tabular}
  \end{table}

>>>>

\subsection{Data}\label{Data}
% 6049 samples - total
% 58 regions
% 10 years
% 
% 853 with reported profits
% 46 regions
% reported since 2018
Data used in this analysis were obtained from Sustainable Winegrowing Australia. Australia's national wine industry sustainability program. The program aims to support grape-growers and winemakers in demonstrating and improving their sustainability \citep{swaSustainableWingrowingAustralia2022}. Data recorded by SWA are entered manually by winegrowers using a web based interface tool. A total of 6049 observations were collected from 2012/2013 to 2021/2022 financial years, with each observation comprising 23 variables reflecting a vineyard's state for the given year (see Table \ref{tab:vars}). 
\par
\begin{table}[] 
 \label{tab:vars}
 \caption{Summary of variables used in the analysis. The recorded column indicate the number of values that were either greater than zero or that were not missing.}\label{tab:summary}
 \begin{tabular}{@{}ccccl@{}}
  \toprule
  \textbf{Variable} & \textbf{Units} & \textbf{Recorded} & \textbf{\begin{tabular}[c]{@{}c@{}}Number of\\ Classes\end{tabular}} & \\ \midrule
  Water Used & Mega Litres & 5846 & & \\
  Diesel & Litres & 5585 & & \\
  Biodiesel & Litres & 25 & & \\
  LPG & Litres & 958 & & \\
  Herbicide Spray & Times per year & 2026 & & \\
  Year & Class & 6049 & 10 & \\
  Disease & Class & 6049 & 2 & \\
  Region & Class & 6049 & 58 & \\
  Solar & Kilowatt Hours & 622 & & \\
  Irrigation Type & Class & 6049 & 20 & \\
  Petrol & Litres & 4309 & & \\
  Slashing & Times per year & 2290 & & \\
  Yield & Tonnes & 5935 & & \\
  Irrigation Energy & Class & 6049 & 16 & \\
  Area Harvested & Hectares & 6049 & & \\
  Electricity & Kilowatt Hours & 1014 & & \\
  Insecticide Spray & Times per year & 1092 & & \\
  Fertiliser & \begin{tabular}[c]{@{}c@{}}Kilograms \\ of Nitrogen\end{tabular} & 795 & & \\
  Fungicide Spray & Times per year & 2260 & & \\
  Cover Crop & Class & 6049 & 32 & \\
  Water Type & Class & 6049 & 39 & \\
  Grape Revenue & AUD & 853 & & \\
  Operating Costs & AUD & 853 & & \\ \bottomrule
  \end{tabular}
\end{table}
The data originally contained only two multiclass variables: year and region. Related binary variables, such as the use of river water and the use of dam water, were combined to create a single multiclass variable. This was done by first converting each combination that occurred into a unique category (such as river and damn water used, as opposed to the two separate categories prior). These variables were then one-hot-encoded, changing each variable class into a binary value, with one indicating the presence of the class and zero indicating its absence. Further details about classes and their frequency is available in the appendices.
\par
The variable region represented one of the 65 Geographical Indicator Regions (GI Region) used to describe different unique localised traits of vineyards across Australia \citep{hallidayAustralianWineEncyclopedia2009,oliverReviewSoilPhysical2013,soarClimateDriversRed2008}. Each region is explicitly defined under the Wine Australia Corporation Act of 1980 \citep{attorney-generalsdepartmentWineAustraliaCorporation2010}.
\par

@@

XGBoosted (eXtreme Gradient Boosting) trees, described in more detail below (and further in the appendix), were created using the XGBoost library \citep{chenXGBoostScalableTree2016} in the Python Programming language \citep{g.vanrossumPythonTutorialTechnical1995}. XGBoosted trees are a boosted tree ensemble method that can be used to classify classes, or predict continuous response variables. They were chosen for this analysis as the data contained a mixture of class and continuous variables. Moreover, XGBoosted trees are unaffected by multicollinearity, and offer high predictive performance for a wide variety of purposes \citep{chenXGBoostScalableTree2016}.

@@

As the purpose of the analysis was to identify relationships between variables and to show how they interact, an XGBoosted tree was created for every variable. Each tree included all variables except the economic variables (operating cost and revenue from grape sales), which were only included within their own trees as response variables. Separately profit (the difference between revenue and operational costs) was looked at in prior analyses (see appendix) but the results were not included due to low average loss values and model stability. This meant that every variable would have a measure of its importance to other variables (see Section \ref{sec:importance}), which was used to show the highly interrelated nature of variables within vineyards. The interaction between variables was illustrated using Sankey and Chord diagrams; with variable importance measures being used to show the strength of connection between the respective predictor variable and the response (see section \ref{sec:importance}).

@@

Due to XGBoost creating a large amount of decision trees, the interpretability of these models is obfuscated by the intricate relationships within complicated ensembles. A measure of variable importance was the technique used to highlight a variables influence within the ensemble. Variable importance can be measured in multiple ways; we used the frequency of a variable appearing as a node within the ensemble as a measure of its importance. This measure was chosen as it connected a variable to the minimisation of its associated objective function. The measure of a variable's importance within this study can then be interpreted as how often a variable was the optimal choice in reducing the loss function of the ensemble. Importantly, multiclass variables being one-hot-encoded (see Section \ref{Data}) are given an importance score for each individual class; for example, each specific region will have its own importance score.

@@

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% The Australian wine-growing industry is a rich and diverse landscape that is separated into multiple Geographical Indicator Regions. Each region describing unique reputations, qualities and varietals of wine produced there. While a great deal has been done regarding individual regional properties and traits, there has been little statistical insight into broader regional comparisons; due to a lack of cross-regional and in-depth data sources \citep{keithjonesAustralianWineIndustry2002,knightFirmResourcesDevelopment2019}. In this study we use Classification Trees to compare regional differences and how these differences relate to sustainable practices. 
% \newline

@@

@@

@@

 \section{Continuous variables}

The Table below shows the ranges of each of the continuous variables:
% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
  \begin{tabular}{@{}lllllllll@{}}
  \toprule
   & count & mean & std & min & 0.25 & 0.5 & 0.75 & max \\ \midrule
  Vineyard Solar & 622 & 22916.89 & 104808 & 1 & 1170.75 & 5500 & 14866.25 & 2300000 \\
  Biodiesel & 25 & 6635.932 & 11768.832104 & 1 & 200 & 500 & 10000 & 37216 \\
  Fungicide Spray & 2260 & 7.724801 & 3.279794 & 1 & 6 & 7 & 9 & 68 \\
  LPG & 958 & 327.831399 & 861.538804 & 1 & 40 & 95.835 & 240 & 11950 \\
  Petrol & 4309 & 825.276809 & 1556.621119 & 1 & 135 & 306.66 & 903 & 38568 \\
  Insecticide Spray & 1092 & 1.707189 & 1.316042 & 0 & 1 & 1 & 2 & 12 \\
  Water Used & 5846 & 7301838 & 558206600 & 0.0007 & 13.2655 & 43 & 146.875 & 42680000000 \\
  Fertiliser & 795 & 91149.89 & 483913.4 & 1 & 560 & 4759.5 & 45148.5 & 11358000 \\
  Diesel & 5585 & 11677.070183 & 24380.588742 & 0.1267 & 1240 & 3850 & 12500 & 591000 \\
  Yield & 5935 & 772.902449 & 2175.113895 & 0.03 & 68 & 192.3 & 601.8795 & 72305 \\
  Herbicide Spray & 2026 & 2.646199 & 2.598899 & 0 & 2 & 2 & 3 & 103 \\
  Slashing & 2290 & 3.311485 & 1.826788 & 1 & 2 & 3 & 4 & 26 \\
  Electricity & 1014 & 58223.07 & 177626.3 & 0.019 & 2160 & 9637 & 36498.25 & 3000000 \\
  Area Harvested & 6049 & 66.52604 & 133.4525 & 2.220446E-16 & 10.13 & 24.5 & 66.8 & 2436.15 \\
  Grape Revenue & 875 & 377972 & 606286.8 & 1 & 76000 & 172964 & 386747 & 5700000 \\
  Operating Costs & 853 & 314187.1 & 511522.6 & 1 & 57315 & 140000 & 327408 & 4482828 \\ \bottomrule
  \end{tabular}
  \end{table}

  \section{Categorical variables}\ref{app: cat_var}
  The tables below describe each possible class a multiclass variable could have taken and the frequency that it occured.
  \subsection{water types}

@@

\subsection{cover crop types}
% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
  \begin{tabular}{@{}ll@{}}
  \toprule
  Cover crop types & frequency \\ \midrule
  permanent_cover_crop_volunteer_sward & 1822 \\
  permanent_cover_crop_non_native & 936 \\
  permanent_cover_crop_native & 490 \\
  annual_cover_crop & 479 \\
  groundwater and surface water dam & 406 \\
  annual_cover_crop and permanent_cover_crop_volunteer_sward & 309 \\
  bare_soil & 225 \\
  permanent_cover_crop_non_native and permanent_cover_crop_volunteer_sward & 214 \\
  annual_cover_crop and permanent_cover_crop_non_native & 169 \\
  bare_soil and permanent_cover_crop_volunteer_sward & 129 \\
  bare_soil and permanent_cover_crop_non_native & 115 \\
  annual_cover_crop and permanent_cover_crop_non_native and permanent_cover_crop_volunteer_sward & 101 \\
  bare_soil and annual_cover_crop & 93 \\
  permanent_cover_crop_native and permanent_cover_crop_volunteer_sward & 80 \\
  bare_soil and permanent_cover_crop_native & 78 \\
  annual_cover_crop and permanent_cover_crop_native & 78 \\
  permanent_cover_crop_native and permanent_cover_crop_non_native & 68 \\
  permanent_cover_crop_native and permanent_cover_crop_non_native and permanent_cover_crop_volunteer_sward & 44 \\
  annual_cover_crop and permanent_cover_crop_native and permanent_cover_crop_non_native and permanent_cover_crop_volunteer_sward & 44 \\
  bare_soil and annual_cover_crop and permanent_cover_crop_volunteer_sward & 33 \\
  bare_soil and permanent_cover_crop_non_native and permanent_cover_crop_volunteer_sward & 26 \\
  annual_cover_crop and permanent_cover_crop_native and permanent_cover_crop_volunteer_sward & 17 \\
  bare_soil and annual_cover_crop and permanent_cover_crop_native & 15 \\
  annual_cover_crop and permanent_cover_crop_native and permanent_cover_crop_non_native & 15 \\
  bare_soil and annual_cover_crop and permanent_cover_crop_non_native & 13 \\
  bare_soil and annual_cover_crop and permanent_cover_crop_native and permanent_cover_crop_non_native and permanent_cover_crop_volunteer_sward & 12 \\
  bare_soil and annual_cover_crop and permanent_cover_crop_non_native and permanent_cover_crop_volunteer_sward & 11 \\
  bare_soil and annual_cover_crop and permanent_cover_crop_native and permanent_cover_crop_non_native & 8 \\
  bare_soil and permanent_cover_crop_native and permanent_cover_crop_non_native & 7 \\
  bare_soil and permanent_cover_crop_native and permanent_cover_crop_volunteer_sward & 6 \\
  bare_soil and permanent_cover_crop_native and permanent_cover_crop_non_native and permanent_cover_crop_volunteer_sward & 4 \\
  bare_soil and annual_cover_crop and permanent_cover_crop_native and permanent_cover_crop_volunteer_sward and & 2 \\ \bottomrule
  \end{tabular}
  \end{table}

\subsection{irrigation type}

@@

  \subsection{irrigation energy type}

@@

  \subsection{year}
  % Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
  \begin{tabular}{@{}ll@{}}
  \toprule
  data_year_id & frequency \\ \midrule
  2021/2022 & 954 \\
  2020/2021 & 860 \\
  2019/2020 & 599 \\
  2012/2013 & 590 \\
  2013/2014 & 549 \\
  2015/2016 & 548 \\
  2014/2015 & 505 \\
  2017/2018 & 493 \\
  2016/2017 & 485 \\
  2018/2019 & 466 \\ \bottomrule
  \end{tabular}
  \end{table}

\subsection{giregion}
% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[]
  \begin{tabular}{@{}ll@{}}
  \toprule
  giregion & frequency \\ \midrule
  McLaren Vale & 1195 \\
  Barossa Valley & 584 \\
  Murray Darling & 521 \\
  Riverland & 472 \\
  Adelaide Hills & 454 \\
  Langhorne Creek & 347 \\
  Margaret River & 344 \\
  Coonawarra & 284 \\
  Padthaway & 202 \\
  Wrattonbully & 195 \\
  Clare Valley & 149 \\
  Yarra Valley & 122 \\
  Eden Valley & 92 \\
  Tasmania & 89 \\
  Swan Hill & 83 \\
  Grampians & 73 \\
  Orange & 72 \\
  Hunter Valley & 70 \\
  Bendigo & 53 \\
  Great Southern & 51 \\
  Rutherglen & 41 \\
  Robe & 36 \\
  Tumbarumba & 35 \\
  Mornington Peninsula & 32 \\
  King Valley & 32 \\
  Southern Fleurieu & 30 \\
  Heathcote & 29 \\
  Adelaide Plains & 25 \\
  Currency Creek & 24 \\
   & 23 \\
  Henty & 22 \\
  Canberra District & 21 \\
  Southern Flinders Ranges & 20 \\
  Upper Goulburn & 20 \\
  Mudgee & 20 \\
  Mount Benson & 20 \\
  Other & 19 \\
  Riverina & 18 \\
  Alpine Valleys & 15 \\
  Barossa Zone & 14 \\
  Pemberton & 12 \\
  Mount Gambier & 11 \\
  Blackwood Valley & 10 \\
  Kangaroo Island & 10 \\
  Big Rivers Zone Other & 9 \\
  Geographe & 7 \\
  Cowra & 6 \\
  Gundagai & 5 \\
  Strathbogie Ranges & 5 \\
  Glenrowan & 4 \\
  Geelong & 4 \\
  Swan District & 4 \\
  Goulburn Valley & 3 \\
  Beechworth & 3 \\
  Southern Highlands & 3 \\
  Macedon Ranges & 2 \\
  Pyrenees & 2 \\
  Sunbury & 1 \\ \bottomrule
  \end{tabular}
  \end{table}
